Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-12-01 leadership_across_cultures_contexts.Rmd

In sum, we aim to empirically and systematically accomplish the following four goals: 1) identify the most cross-culturally frequent qualities of leaders and the functions they serve; 2) identify features of the qualities and functions of leaders in reference to theoretical models or novel interpretations; 3) identify the most cross-culturally frequent costs and benefits of leadership for both leaders and followers; and 4) explore relationships between measures of leader qualities and functions with group structure and population-level measures.

>>>>

In sum, we aim to answer the following questions: 1) what are the most frequent qualities of leaders across cultures? 2) What functions are leaders most commonly serving across cultures? 3) What "features" exist in our data, e.g., do particular variables tended to covary or cluster together? Such features might lend support to existing theories; for instance they might correspond to "prestige" and "dominance" [@henrich_evolution_2001]. Or they might suggest new and theoretically important dimensions of leadership. 4) What are the most salient costs and benefits of leadership for both leaders and followers? And 5) how does variation across these measures relate to population-level variation?
